---
title: "EEEB UN3005/GR5005  \nLab - Week 04"
author: "USE YOUR NAME HERE"
output: pdf_document
fontsize: 12pt
---
  
```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(rethinking)

# Knit option to cut long lines of code
require('formatR')
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 80), tidy = TRUE)

```


# Descriptive statistics of fox data

NOTE: For all parts of this lab, please make sure you label your plots appropriately with axis labels and titles! 


For the first part of this week's lab, we'll be using data on foxes occupying urban England. You can access this data once you've loaded the `rethinking` package with the code `data(foxes)`. You can get a brief summary of all the variables contained in the dataset using `?foxes` or a data frame summary function of your choice. We will be re-using this dataset again later in semester and explore it using Bayesian tools. 




## Exercise 1 (2 points): empirical cumulative distribution function

Using the function `ecdf` plot an empirical  cumulative distribution function for weight (1 point). What is the weight that captures about 95% of all foxes in this dataset? (1 point) (2 points total)

```{r}


```






## Exercise 2 (5 points): Histogram, density plot, and custom normal distribution

Make a histogram of fox weights with a function of your choice (1 point) . 
Calculate the mean and standard deviation (1 point). 
Plot the density distribution using `geom_density()` in a separate plot (1 point). 
On top of this plot, show the normal distribution with the calculated mean and standard deviation in a different color (1 point). 
Is your distribution approximately normal? (1 point)

```{r}


```




## Exercise 3 (5 points): Bar chart with error bars

Asses graphically whether group size is related to the average food obtained by the foxes as a measure of hunting success. 
To do so, summarize your data to calculate the mean avgfood for each group size. (1 point)
Create a bar chart with group size on the x-axis, and mean avgfood on the y-axis. (2 points)
Add the standard deviation of avgfood at each group size as an error bar to each bar. (1 point)
What do the data suggest about this relationship? (1 point)

```{r}



```





# Descriptive statistics of behavioral risk factor data

Let's switch geats and use a new dataset to do some more complex graphing. 
Import data from the Behavioral Risk Factor Surveillance System (BRFSS), which is a telephone survey of 20,000 individuals conducted by the CDC in 2000.   

```{r}
source("http://www.openintro.org/stat/data/cdc.R")

```





## Exercise 4: Grouped bar chart (7 points)

Assess whether there is a potential association between smoking status (variable `smoke100`) and general health status (`genhlth`) among the people surveyed. 
To do this, create a grouped bar chart of the proportion of all survey participants in each general health status (poor, fair, etc.) that fall into the 'smoker' category (`smoke100` == 1). Carefully think about how you want to set up this graph. Your main interest is in compariong smoker vs. non-smoker and evaluate if their general health differs. This should determine what variable goes on the x-axis and which one is used as a grouping variable. (5 points)

Based on your graph, what do you conclude about the relationship between smoking status and general health? Describe at least 2 patterns of interest that you can tell from this visual representation of the data. (2 points)

Note: Check your variable data type and note that to act as a grouping variable, the variable should be in character or factor format. Also, carefully think about how to calculate percentages (what is your denominator?) to best answer the question. 

```{r}


  

```





  
  
## Exercise 5 (6 points): Grouped bar chart with faceting

Your result from exercise 4 could be confounded in various ways. For example, perhaps smokers are more likely to fall into lower socioeconomic groups and thefore are less likely to be covered by health insurance, captured in the variable `hlthplan`. Create the same figure as in the previous exercise but now calculate percentages with the additional grouping of `hlthplan` and then facet the plot by whether or not people have health coverage. (4 points)

What do you conclude? (2 points)

```{r}




```




